Inference methods comparison for the simplified Naomi model

### 2023-03-08 src/naomi-simple_compare/comparison.Rmd
Save beta_anc_rho too

The `beta_rho` parameter is used in other reports as a check, so create the dataframe to save as artefact here:

```{r}
beta_rho <- histogram_and_ecdf("beta_rho", i = 1, return_df = TRUE)
saveRDS(beta_rho$df, "beta_rho.rds")
```

>>>>

The `beta_rho` and `beta_anc_rho` parameters are used in other reports, so create dataframes here to save as artefacts:

```{r}
beta_rho <- histogram_and_ecdf("beta_rho", i = 1, return_df = TRUE)
saveRDS(beta_rho$df, "beta_rho.rds")

beta_anc_rho <- histogram_and_ecdf("beta_anc_rho", return_df = TRUE)
saveRDS(beta_anc_rho$df, "beta_anc_rho.rds")
```
